---
title: "Assignment 2 - Titanic Dataset"
output:
  html_document: default
  pdf_document: default
---
``` {r}
#reading the data in
data1<-read.csv("C:\\Users\\Lenovo\\Desktop\\stats-assignment 2\\titanic.csv")
``` 


1. Is there a significant difference in Age distribution between those who survived and
   those who did not?

Null Hypothesis: There is no significant difference between the two distribution of the ages.
Alternative Hypothesis : There is a significant difference between the two distribution of the ages.


``` {r}

#having a table for age and survival
asu <- data.frame(data1$Age,data1$Survived)
#Dividing Survived and Not Survived
asu0<-subset(asu,asu$data1.Survived==1)
asu1<-subset(asu,asu$data1.Survived==0)
```

Boxplot
``` {r}
boxplot(asu0$data1.Age,asu1$data1.Age)
```
Histogram
``` {r}
hist(asu0$data1.Age,main = 'histogram of Age - Not Survived',xlab = 'Age')

```

``` {r}
hist(asu1$data1.Age,main = 'histogram of Age - Survived',xlab = 'Age')

```
``` {r}
qqnorm(asu0$data1.Age,main = "QQ Normal plot for Age - Not Survived")

```
``` {r}
qqnorm(asu1$data1.Age,main = "QQ Normal plot for Age - Survived")
```
Conducting Normality test for both the samples

``` {r}
normtest<-function(x)
{
  library(nortest)
  s<-shapiro.test(x)
  ad<-ad.test(x)
  cvm<-cvm.test(x)
  ll<-lillie.test(x)
  sf<-sf.test(x)
  df<-data.frame(Method=c(s$method, ad$method, cvm$method, ll$method, sf$method),
                 P.Value=c(s$p.value, ad$p.value, cvm$p.value, ll$p.value, sf$p.value))
  df
}

normtest(asu0$data1.Age)
```
```{R}
normtest(asu1$data1.Age)
```

```{R}
ks.test(asu0$data1.Age,asu1$data1.Age)
```
Two sample Kolmogrov Smirov test was to survived and not survived. 
There was a significant difference in Age distribution between those who survived and those who did not.


------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------

2.  Answer the same as above after controlling for Gender.


```{R}
#Controlling for gender in the age table
gsu <- data.frame(data1$Gender,data1$Age,data1$Survived)
#Dividing Survived and Not Survived
gsu0<-subset(gsu,gsu$data1.Survived==0)
gsu1<-subset(gsu,gsu$data1.Survived==1)
```

Barplot for Not Survided people

```{R}
barplot(table(gsu0$data1.Gender))
```
Barplot for Survived People

```{R}
barplot(table(gsu1$data1.Gender))
```

```{R}
#Dividing the table for gender
msu0<-subset(gsu0,gsu0$data1.Gender=='male')
fsu0<-subset(gsu0,gsu0$data1.Gender=='female')
msu1<-subset(gsu1,gsu1$data1.Gender=='male')
fsu1<-subset(gsu1,gsu1$data1.Gender=='female')
```

Box Plot
```{R}
boxplot(msu0$data1.Age,msu1$data1.Age,fsu0$data1.Age,fsu1$data1.Age,main='Male not survived vs Male Survived vs Female Not Survived vs Female Survived')
```

```{R}
hist(msu0$data1.Age,main = 'histogram of Age - Not Survived - Male',xlab = 'Age')
```
```{R}
hist(msu1$data1.Age,main = 'histogram of Age -  Survived - Male',xlab = 'Age')
```

```{R}
hist(fsu0$data1.Age,main = 'histogram of Age - Not Survived - Female',xlab = 'Age')
```

```{R}
hist(fsu1$data1.Age,main = 'histogram of Age - Survived - Female',xlab = 'Age')
```

```{R}
qqnorm(msu0$data1.Age,main = "QQ Normal plot for Age - Not Survived - Male")

```

```{R}
qqnorm(msu1$data1.Age,main = "QQ Normal plot for Age -  Survived - Male")
```

```{R}
qqnorm(fsu0$data1.Age,main = "QQ Normal plot for Age - Not Survived - Female")
```

```{R}
qqnorm(fsu1$data1.Age,main = "QQ Normal plot for Age -  Survived - Female")
```
Normality test for both the samples

```{R}
normtest(msu0$data1.Age)
```

```{R}
normtest(msu1$data1.Age)
```

```{R}
normtest(fsu0$data1.Age)
```

```{R}
normtest(fsu1$data1.Age)
```

All the Distributions are Not Normal

```{R}
ks.test(msu0$data1.Age,msu1$data1.Age)
```

```{R}
ks.test(fsu0$data1.Age,fsu1$data1.Age)
```

There is a significant difference between the ages in the survived rate of Male and Female.

--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------

3. Remark on how Age affected the Survival Probability of a passenger on board the
   Titanic, based on consolidations of your findings in 1 and 2 above
   
```{R}
#copy to staging table
asuc1<-asu1
asuc0<-asu0
asuc0<-cut(asuc0$data1.Age,c(0,18,30,55,150))
asuc1<-cut(asuc1$data1.Age,c(0,18,30,55,150))

x<-table(asuc1)
y<-table(asuc0)

x<-data.frame(t(t(table(asuc1))))
y<-data.frame(t(t(table(asuc0))))
x<-x[-2]
y<-y[-2]
#combining tables
AgeTable<-cbind(x,y$Freq)

#renaming columns
names(AgeTable)[names(AgeTable) == "asuc1"] <- "def"
names(AgeTable)[names(AgeTable) == "Freq"] <- "Survived"
names(AgeTable)[names(AgeTable) == "y$Freq"] <- "Un-Survived"
rownames(AgeTable)<-c("Young","Young Adult","Adult","Old")
AgeTable
```

```{R}
#Proportion - Survival Rate
AgeTable<-AgeTable[-1]
#margin.table(AgeTable)
AgeTable

```
